\documentclass[a4paper]{article}

% Import some useful packages
\usepackage[margin=0.5in]{geometry} % narrow margins
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{hyperref}
\usepackage{minted}
\usepackage{amsmath}
\usepackage{xcolor}
\definecolor{LightGray}{gray}{0.95}

\title{Peer-review of assignment 6 for \textit{INF3331-ReviewedRepo}}
\author{Reviewer 1, Git-repo INF3331-Daniel, {danielfolgero@gmail.com},\\ The other reviewers didn't need to do this exercise.}
\date{Deadline: Tuesday, 8. December 2015, 23:59:59.}

\begin{document}
\maketitle

\section{Review}\label{sec:review}

Windows 8.1  with Python 2.7.10 and the linux machines on ifi.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 6.1: Feed line to Python}
Working as intended. \\
Good amount of comments and nice docstring.\\
Clean, but compact code. It wouldn't hurt with a few more spaces.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 6.2: Create basic interface} \label{sec:assignment6.2}
Works as intended.\\
good docstring, nice amount of comments.\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 6.3: Error handling}
Works as intended

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 6.4:  Control sequence}
Works as intended.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 6.5: Up and down characters and command history}
Works as intended.\\
There is a lot of very similar code repeated here which maked me think you could have made a method or had 
some code outside the if/else to get less and cleaner code.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 6.6: Magic commands}
Works as intended.\\
Good amount of comments.\\
Look at the comment in 6.7 regarding displaying docstrings.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 6.7: Webinterface}
I didn't get Flask to work on the linux machines on Ifi so I couln't test this.\\
It looks like it will work fine tho.\\
A few points here:\\
- You could have put the html code in templates which would have made the code a bit more tidy, but this was not required.\\
- I didn't get to test it, but i suspect the webinterface will crash if you try to display the docstrings
  from the webinterface since you dont return a string with the docstring but prints it out with the command
  window which have to be exited by q.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 6.8: Tab completion}
Works as intended.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 6.9: Backspace}
Works as intended.


\bibliographystyle{plain}
\bibliography{literature}

\end{document}